Models

### 2023-02-09 analysis/05_model_metrics.Rmd
clean up

  if (missing(filter_study_id)){
    fit_data <- data %>%
      filter(metric == metric_name) %>%
      mutate(year_scaled = scale(year),
             duration_scaled = scale(duration, scale = FALSE),
             startyear_scaled = scale(startyear, scale = FALSE),
             taxa = as.factor(taxa),
             realm = as.factor(realm),
             climate = as.factor(climate))
  } else{
    print("Filter study")

@@

# get dataframe of mixed effects models to fit
metric_df <- bind_rows(tibble(metric_name = raw_metrics, 
                         formula = "value ~ year_scaled + (year_scaled|rarefyID)"),
          tibble(metric_name = logone_metrics, 
                         formula = "logvalue ~ year_scaled + (year_scaled|rarefyID)"),
          tibble(metric_name = log_metrics, 
                         formula = "log(value) ~ year_scaled + (year_scaled|rarefyID)")) %>%
  mutate(model_id = "base")

# exclude studies/metrics with only one rarefyID
mixed_indv_model_df <- map_dfr(unique(model_data$study_id), ~metric_df %>% mutate(filter_study_id = .x)) %>%
  anti_join(single_ts, by = c("metric_name", "filter_study_id"))

@@

##FIXME: some of these still don't converge##
```

@@

bootstrap_study_slopes <- function(metric, model, model_id, nsim){
  browser()
  print(c(metric, model_id))

@@

bootstrap_slopes <- pmap_dfr(model_df %>% filter(model_id == "base", metric == "CWM_bodymass_value") %>% mutate(nsim = 100), bootstrap_study_slopes) %>%
  # furrr::future_pmap_dfr(model_df %>% filter(model_id == "base") %>% mutate(nsim = 100), bootstrap_study_slopes, 
  #                                          .options = furrr::furrr_options(seed = TRUE)) %>%
  mutate(upr.ci = estimate + (2*std.error),
         lwr.ci = estimate - (2*std.error),
         sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ FALSE,
             TRUE ~ TRUE
           ))

slope_comp <- study_slopes %>% 
  select(study_id, metric, sig_bulp = sig) %>%
  left_join(bootstrap_slopes %>% 
              select(study_id, metric, sig_boot = sig)) %>%
  left_join(indv_mod_results %>%
              filter(term == "year_scaled") %>%
            mutate(sig_indv = if_else(p.value < 0.05, TRUE, FALSE)) %>%
              select(study_id, metric, sig_indv))
```

>>>>

  if (missing(filter_study_id)){
    fit_data <- data %>%
      filter(metric == metric_name) %>%
      mutate(year_scaled = scale(year),
             duration_scaled = scale(duration, scale = FALSE),
             startyear_scaled = scale(startyear, scale = FALSE),
             taxa = as.factor(taxa),
             realm = as.factor(realm),
             climate = as.factor(climate))
  } else{
    print(paste("Filter study", filter_study))

@@

# get dataframe of mixed effects models to fit
metric_df <- model_data %>%
  select(filter_study_id = study_id, metric_name = metric) %>% 
  distinct() %>% 
  mutate(model_id = "base",
         formula = case_when(
           metric_name %in% raw_metrics ~ "value ~ year_scaled + (year_scaled|rarefyID)",
           metric_name %in% log_metrics ~ "log(value) ~ year_scaled + (year_scaled|rarefyID)",
           TRUE ~ "logvalue ~ year_scaled + (year_scaled|rarefyID)"
           )
         )

# exclude studies/metrics with only one rarefyID
mixed_indv_model_df <- metric_df %>%
  anti_join(single_ts, by = c("metric_name", "filter_study_id"))

@@

# There are 12 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
# tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()
# 
# pmap_df(tofit_mods %>% select(metric_name = metric, filter_study_id = study_id), function(metric_name, filter_study_id) {model_data %>% 
#          filter(metric_name == metric, study_id == filter_study_id) %>%
#         mutate(n = n(), nrarefyID = n_distinct(rarefyID)) %>%
#         select(metric, study_id, nrarefyID, n) %>%
#         distinct()}) %>% View()

@@

bootstrap_study_slopes <- function(metric, model, model_id, nsim){

  print(c(metric, model_id))

@@

bootstrap_slopes <- pmap_dfr(model_df %>% filter(model_id == "base") %>% mutate(nsim = 100), bootstrap_study_slopes) %>%
  # furrr::future_pmap_dfr(model_df %>% filter(model_id == "base") %>% mutate(nsim = 100), bootstrap_study_slopes, 
  #                                          .options = furrr::furrr_options(seed = TRUE)) %>%
  mutate(upr.ci = estimate + (2*std.error),
         lwr.ci = estimate - (2*std.error),
         sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ FALSE,
             TRUE ~ TRUE
           ))

slope_comp <- study_slopes %>% 
  select(study_id, metric, sig_bulp = sig) %>%
  left_join(bootstrap_slopes %>% 
              select(study_id, metric, boot_estimate = estimate, boot_stde = std.error, sig_boot = sig)) %>%
  left_join(indv_mod_results %>%
              filter(term == "year_scaled") %>%
            mutate(sig_indv = if_else(p.value < 0.05, TRUE, FALSE)) %>%
              select(study_id, metric, indv_estimate = estimate, indv_stde = std.error, sig_indv))
```
